\documentclass[titlepage]{article}

\author{Bryant Eisenbach}
\title{Note Analyzer}
\def\project{Note Analyzer }

\def\authorship{B. Eisenbach (bje2113)}
\input{formatting.tex}

\begin{document}

%\input{background.tex}

\section{Prototype Updates}
Since the Proposal, the Prototype phase has numerous updates to the methodology section.
For simplicity of review, only the methodology section is included below.
Please review the Proposal for the Abstract and Background sections about this project,
which will be included in the Final Report.
An assumption is made that familiarity with the project is a given.

\section{Methodology}
\input{methodology.tex}

\pagebreak
\section{Current Status}
Due to the time spent getting the guitar and hand classifiers to work,
little time was spent on the guitar and hand modeling algorithms,
and subsequently the end goal of the guitar note prediction algorithm is incomplete.
Once the classifiers are working reliably, the next step will be to show that
the hand model algorithm can consistently identify the locations of the fingertips,
and that the guitar model can accurately model the location of guitar frets and strings
in order to match the two together with motion processing algorithms to detect discrete
string pluck events.

Additionally, future progress will initially be focused on getting the
author's bass guitar to be recognized by the classifier
(along with the author's hands and playing style, as well as enviromental conditions such as clothing and background choice).
Once the pipeline is working reliably, additional player(s) and/or bass guitar(s) will
be attempted. If time permits, perhaps the author's acoustic guitar will be attempted as well.

\bibliography{bibliography.bib}{}
\bibliographystyle{plain}

\end{document}
